Measurement and Probability in Fuzzy Quantum Theories

### 2017-04-11 prop_iop.tex
prop_iop.tex \section{Expectation Values for IVPMs} Updating...

As motivated above, an event $E_{1}$ may have an interval of probability
$[l_{1},r_{1}]$. Assume that another disjoint event $E_{2}$ has
an interval of probability $[l_{2},r_{2}]$, what is the interval
of probability for the event $E_{1}\cup E_{2}$? The answer is somewhat
subtle: although it is possible to use the sum of the intervals $[l_{1}+l_{2},r_{1}+r_{2}]$
as the combined probability, one can find a much tighter interval
if information \emph{against} the event (i.e., information about the
complement event) is also taken into consideration. Formally, for
a general event $E$ with probability $[l,r]$, the evidence that
contradicts $E$ is evidence supporting the complement of $E$. The
complement of $E$ must therefore have probability $\left[1-r,1-l\right]$
which we abbreviate $\left[1,1\right]-\left[l,r\right]$. Given a
sample space~$\Omega$, its set of events~$\events$, and a collection
of intervals $\mathscr{I}$, a function~$\bar{\mu}:\events\rightarrow\mathscr{I}$
is a classical interval-valued probability measure if and only if
$\bar{\mu}$ satisfies the following conditions~\cite{JamisonLodwick2004}
where the last line uses $\subseteq$ to allow for tighter intervals
that exploit the complement event: 
\begin{itemize}
\item $\bar{\mu}(\emptyset)=[0,0]$. 
\item $\bar{\mu}(\Omega)=[1,1]$. 
\item For any event $E$, $\bar{\mu}\left(\Omega\backslash
E\right)=\left[1,1\right]-\bar{\mu}\left(E\right)$.
\item For a collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise disjoint
events, we have 
\begin{equation}
\bar{\mu}\left(\bigcup_{i=1}^{N}E_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(E_{i}\right)\textrm{ .}\label{eq:classical-include}
\end{equation}
\end{itemize}

@@

>>>>

As motivated above, an event $E_{1}$ may have an interval of probability
$[l_{1},r_{1}]$. Assume that another disjoint event $E_{2}$ has
an interval of probability $[l_{2},r_{2}]$, what is the interval
of probability for the event $E_{1}\cup E_{2}$? The answer is somewhat
subtle: although it is possible to use the sum of the intervals $[l_{1}+l_{2},r_{1}+r_{2}]$
as the combined probability, one can find a much tighter interval
if information \emph{against} the event (i.e., information about the
complement event) is also taken into consideration. Formally, for
a general event $E$ with probability $[l,r]$, the evidence that
contradicts $E$ is evidence supporting the complement of $E$. The
complement of $E$ must therefore have probability $\left[1-r,1-l\right]$
which we abbreviate $\left[1,1\right]-\left[l,r\right]$. Given a
sample space~$\Omega$, its set of events~$\events$, and a collection
of intervals $\mathscr{I}$, a function~$\bar{\mu}:\events\rightarrow\mathscr{I}$
is a classical interval-valued probability measure if and only if
$\bar{\mu}$ satisfies the following conditions~\cite{JamisonLodwick2004}
where the last line uses $\subseteq$ to allow for tighter intervals
that exploit the complement event: 
\begin{itemize}
\item $\bar{\mu}(\emptyset)=[0,0]$. 
\item $\bar{\mu}(\Omega)=[1,1]$. 
\item For any event $E$, 
\begin{equation}
\bar{\mu}\left(\Omega\backslash E\right)=\left[1,1\right]-\bar{\mu}\left(E\right)\textrm{ .}\label{eq:classical-complement}
\end{equation}
\item For a collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise disjoint
events, we have 
\begin{equation}
\bar{\mu}\left(\bigcup_{i=1}^{N}E_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(E_{i}\right)\textrm{ .}\label{eq:classical-include}
\end{equation}
\end{itemize}

@@

Consider the random variable~$X$ representing the number of tails.
For the probability measure~$\pmeas$ in example~\ref{ex1}, the
expectation value of $X$ is
\begin{eqnarray*}
\int X\rmd\pmeas & = & 0\cdot\pmeas(\{HH\})+1\cdot\pmeas(\{HT,TH\})+2\cdot\pmeas(\{TT\})\\
 & = & 0\cdot\frac{1}{3}+1\cdot\frac{2}{3}+2\cdot0=\frac{2}{3}\textrm{ .}
\end{eqnarray*}
Now consider the IVPM~$\bar{\mu}$ in example~\ref{ex3}. First,
since the left-end and the right-end satisfies equation~(\ref{eq:classical-complement})
